Blockchain System

### 2020-11-25 papers/execution-model/model.tex

\begin{definition}%[State of a node]
  The \emph{state of a node} is a tuple
  $\NODE = [\ACCOUNTS, \OPERATIONS]$, where $\ACCOUNTS$ is a set of
  accounts and
  $\OPERATIONS$ is a set of operations.
\end{definition}

@@

\begin{definition}%[Query]
A \emph{query} is defined by the following grammar:
\begin{align*}
  \QRY & ::= \GETBALANCE\ADDR
  \\&\mid \GETSTATUS\OPH
  \\&\mid \GETSTORAGE\PUH
  \\&\mid \GETCODE\PUH 
  \\&\mid \GETCOUNTER\PUK
\end{align*}

\end{definition}

When an operation is injected in a node, it enters a \emph{pending pool}
(and is called a \emph{pending operation}). 
 \begin{definition}%[Pending operation]
A \emph{pending operation} is a tuple  $\langle  \OP, \OPH, \TIME
\rangle $, where $\OP$ is an operation, $\OPH$ is the operation hash,
and $\TIME$ is the time when the operation was injected. 
\end{definition}
After some time, a pending operation may be included in the blockchain as an accepted operation.
%Let \textit{P} is the set of pending operations.
 \begin{definition}%[Accepted operation]
An \emph{accepted operation}  is a tuple $\langle  \OP, \OPH, \TIME, \TIME' \rangle
$, where $\OP$ is an operation, $\OPH$ is the operation hash, $\TIME$ is the time when the operation was injected, and
$\TIME'$ is the time when it was included in the blockchain. 
\end{definition}

@@

\begin{mathpar}
  \inferrule[Node-Op]
  { % \CHECKACC (\OP.\PUK, \ACCOUNTS)
    \Angle{\PAK,\OP.\PUK} \in \ACCOUNTS
    % \\
    % \OP = \TRANSFER[\STRING]\NTEZ\PUK{\PUK'}\MTEZ
  }{
    [\ACCOUNTS, \OPERATIONS]
    \NodeTrans
    [\ACCOUNTS, \OP:: \OPERATIONS]
  }

@@

      (\MANAGERS, \PUK, \NTEZ, \MTEZ), \\ \Angle{\GENERATEHASH(\CODE, \INIT, \TIME, \TIME'), \NTEZ, \CODE, \UPDATESTORAGE(\STRING, '', '')} :: \CONTRACTORS, \TIME'+1]

@@

    \QRY = \GETBALANCE\PUK \\

@@

  }{\BAL}

@@

    \QRY = \GETBALANCE\PUH \\

@@

  }{\BAL}

@@

    \QRY = \GETSTORAGE\PUH \\

@@

  }{\STORAGE}

@@

  }{\CODE}

@@

    \QRY = \GETCOUNTER\PUK \\

@@

  }{\COU}

@@

    \QRY = \GETSTATUS\OPH \\

@@

  }{\STATUSPENDING}

@@

  }{\STATUSINCLUDING}

@@

    \item Function  \UPDATECONSTR (\CONTRACTORS, \PUH, \NTEZ, \STRING) updates the contractor that associates with the public hash \PUH\, where
    \begin{itemize}
        \item[] $\langle  \PUH, \BAL, \CODE, \STORAGE, \rangle $ $\Rightarrow$ $\langle  \PUH, \BAL + \NTEZ, \CODE, \\ \UPDATESTORAGE(\STORAGE,\CODE,\STRING) \rangle $
    \end{itemize}

>>>>

\begin{definition}%[Query]
\emph{Queries} are defined by the following grammar:
\begin{align*}
  \QRY & ::= \GETBALANCE\ADDR
  \\&\mid \GETSTATUS\OPH
  \\&\mid \GETSTORAGE\PUH
  \\&\mid \GETCODE\PUH 
  \\&\mid \GETCOUNTER\PUK
\end{align*}
\end{definition}

\begin{definition}%[Program]
\emph{Programs} are defined by the following grammar:
\begin{align*}
	\PROGRAM & :: =  \VARIABLE\ \mid \VALUE \mid \lambda \VARIABLE \PROGRAM\ 
	\\&\mid \PROGRAM\PROGRAM\ \mid (\PROGRAM,\PROGRAM) 	%\mid \NI \EI
	\\&\mid \PROGRAM\ \PLUS\ \PROGRAM\ \mid \PROGRAM\ \MINUS\ \PROGRAM\ \mid \PROGRAM\ \EQUAL\ \PROGRAM\ \mid \PROGRAM\ \LESS\ \PROGRAM
	\\&\mid \PROGRAM\ \AND\ \PROGRAM\ \mid \PROGRAM\ \OR\ \PROGRAM\ \mid \NOT\ \PROGRAM
	\\&\mid \NIL\ \mid \CONS\ \PROGRAM \PROGRAM
	\\&\mid \lambda \VARIABLE\QRY
\end{align*}
\end{definition}

\begin{definition}%[State of a node]
  The \emph{state of a node} is a tuple
  $\NODE = [ \PROGRAMS, \ACCOUNTS, \OPERATIONS]$, where $\PROGRAMS$ is the set of the programs, $\ACCOUNTS$ is a set of
  accounts, and
  $\OPERATIONS$ is a set of operations.
\end{definition}

@@

When an operation is injected in a node, it enters a \emph{pending pool}
(and is called a \emph{pending operation}).

 \begin{definition}%[Pending operation]
A \emph{pending operation} is a tuple  $\langle  \OP, \OPH, \TIME
\rangle $, where $\OP$ is an operation, $\OPH$ is the operation hash,
and $\TIME$ is the time when the operation was injected. 
\end{definition}

After some time, a pending operation may be included in the blockchain as an accepted operation.

 \begin{definition}%[Accepted operation]
An \emph{accepted operation}  is a tuple $\langle  \OP, \OPH, \TIME, \TIME' \rangle
$, where $\OP$ is an operation, $\OPH$ is the operation hash, $\TIME$ is the time when the operation was injected, and
$\TIME'$ is the time when it was included in the blockchain. 
\end{definition}

@@

\begin{mathpar}
  \inferrule[Node-Op]
  {
    \Angle{\PAK,\OP.\PUK} \in \ACCOUNTS
  }{
    [\PROGRAMS, \ACCOUNTS, \OPERATIONS]
    \NodeTrans
    [\PROGRAMS, \ACCOUNTS, \OP:: \OPERATIONS]
  }

  \inferrule[Node-Oph]
  {
   \\
  }{
    [\epsilon[\OP] :: \PROGRAMS, \ACCOUNTS, \OPERATIONS]
    \NodeTrans
    [\epsilon[\OPH] :: \PROGRAMS, \ACCOUNTS, \OPERATIONS]
  }

@@

      (\MANAGERS, \PUK, \NTEZ, \MTEZ), \\ \Angle{\GENERATEHASH(\CODE, \INIT, \TIME, \TIME'), \NTEZ, \CODE, \STRING} :: \CONTRACTORS, \TIME'+1]

@@

    \BLOCKCHAIN = 

@@

  }{[\epsilon[\GETBALANCE\PUK] :: \PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
    \NodeTrans [\epsilon[\BAL] ::\PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}

@@

@@

  }{[\epsilon[\GETBALANCE\PUH] :: \PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
    \NodeTrans [\epsilon[\BAL] ::\PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}

@@

@@

  }{[\epsilon[\GETSTORAGE\PUH] :: \PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
    \NodeTrans [\epsilon[\STORAGE] ::\PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}

@@

  }{[\epsilon[\GETCODE\PUH] :: \PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
    \NodeTrans [\epsilon[\CODE] ::\PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}

@@

@@

  }{[\epsilon[\GETCOUNTER\PUK] :: \PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
    \NodeTrans [\epsilon[\COU] ::\PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}

@@

@@

  }{[\epsilon[\GETSTATUS\OPH] :: \PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
    \NodeTrans [\epsilon[\STATUSPENDING] ::\PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}

@@

  }{[\epsilon[\GETSTATUS\OPH] :: \PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
    \NodeTrans [\epsilon[\STATUSINCLUDING] ::\PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}

@@

    \item Function  \UPDATECONSTR (\CONTRACTORS, \PUH, \NTEZ, \PARAMETER) updates the contractor that associates with the public hash \PUH\, where
    \begin{itemize}
        \item[] $\langle  \PUH, \BAL, \CODE, \STORAGE, \rangle $ $\Rightarrow$ $\langle  \PUH, \BAL + \NTEZ, \CODE, \\ \UPDATESTORAGE(\STORAGE,\CODE,\PARAMETER) \rangle $
    \end{itemize}
